lab_notebook

### 2018-11-25 lab_notebook.Rmd
playing with fishbase
making sure scripts run and are organized and adding species_rightsbased file

@@

@@

>>>>

#write.csv(true_turf_itq_iscaap, file = "true_turf_itq_iscaap.csv")

@@

growth <- popgrowth(species)

@@

FAO website with fisheries data is currently unavaliable. Updated by hand for now; read in below 
```{r}
species_rightsbased <- read_csv("processed_data/species_rightsbased.csv")
```
-	used FAO 3-Alpha species codes (ASFIS) updated 2/2009
-	ones with no ISSCAPP # still are shellfish, snails, crabs, not species specific, common name, species in NA, or a family name with more than 1 #
